Generating Images From Captions\\ With Attention

### 2015-10-07 ram_workshop/ram-paper.tex
update ram workshop

\documentclass{article} % For LaTeX2e
\usepackage{iclr-style/iclr2016_conference,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{subfig}
\usepackage{tabulary}
\usepackage{soul}
\usepackage{color}
\usepackage{xcolor}

@@

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\begin{document}

@@

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\end{center}
\caption{Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages1}
\vspace{-0.3cm}
\end{figure}

@@

\subsubsection{Analysis of Attention}
Unfortunately, we found that there was no connection between the patches drawn on canvas and most attended words at each timestep. During the image generation, the model mostly focused on several words that carried the semantic meaning of caption. The words which were mostly attended during all generation steps indicated the kind of scene the model would generate. For example, as shown in Figure~\ref{fig:attentimages1} by equally looking at words deset and forest allowed the model to make relevant changes in the scene. Whereas in the second example, the model completely ignored word sun and didn't make any changes.

\begin{figure}[!h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{desert}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-sharp.png}}\quad
%
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{forest}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-sharp.png}}\quad
%
\subfloat[\hlctwo{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlctwo{beach}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-sharp.png}}\quad
%
\subfloat[\hlcthree{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlczero{sun}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-sharp.png}}\quad
%
\end{center}
\caption{Examples of most attended words while changing the background in the caption.}
\label{fig:attentimages1}
\vspace{-0.3cm}
\end{figure}

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c}
\hline
\multicolumn{7}{c}{\textbf{COCO (before sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Search} & Image Similarity \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 \\ % - & - & - & - & - & 0.08
\hline
Fully-conn. VAE (L2 cost) & 1.0 & 5.6 & 10.4 & 51.1 & 51 & 0.156 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv. VAE (L2 cost) & 1.0 & 5.9 & 10.9 & 50.8 & 50 & \textbf{0.164} \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
Skipthought DRAW & 2.0 & 11.2 & 18.9 & 63.3 & 36 & 0.157 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
Noalign DRAW & 2.8 & \textbf{14.1} & \textbf{23.1} & 68.0 & \textbf{31} & 0.155 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
Align DRAW & \textbf{3.0} & 14.0 & 22.9 & \textbf{68.5} & \textbf{31} & 0.156 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\end{table}

% \begin{table}[!t]
% \begin{center}
% \begin{tabulary}{\linewidth}{c || c c c c c || c}
% \hline
% \multicolumn{7}{c}{\textbf{COCO (before sharpening)}} \\
% \hline
% & \multicolumn{5}{c||}{Image Search} & Image Similarity \\
% %\cline{2-6}
% \textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI} \\
% \hline
% \hline
% LAPGAN & - & - & - & - & - & 0.08 \\ % - & - & - & - & - & 0.08
% \hline
% Fully-conn. VAE (L2 cost) & 0.7 & 4.6 & 8.7 & 46.8 & 54 & 0.122 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
% Conv. VAE (L2 cost) & 0.7 & 4.4 & 8.5 & 46.6 & 54 & \textbf{0.131} \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
% Noalign DRAW & \textbf{1.0} & 6.1 & 11.2 & 52.1 & \textbf{48} & 0.114 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
% Skipthought DRAW & \textbf{1.0} & \textbf{6.2} & \textbf{11.5} & \textbf{52.5} & \textbf{48} & 0.118 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
% Align DRAW & 0.9 & \textbf{6.2} & 11.2 & \textbf{52.5} & \textbf{48} & 0.115 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
% \end{tabulary}
% \end{center}
% \end{table}

\bibliography{iclr-paper}
\bibliographystyle{iclr-style/iclr2016_conference}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{subfig}
\usepackage{tabulary}
\usepackage{soul}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{natbib}
%\usepackage[style=numeric,sorting=none,maxnames=2]{natbib}
\usepackage[square,comma,sort&compress,numbers]{natbib} 
\bibliographystyle{unsrt85}

@@

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\graphicspath{{../}}
\begin{document}

@@

\begin{figure}[!h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\end{center}
\caption{Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages1}
\vspace{-0.3cm}
\end{figure}

@@

\subsubsection{Analysis of Attention}

Unfortunately, we found that there was no real connection between the patches drawn on canvas and most attended words at each timestep. During the generation, the model mostly focused on several words that were represented the idea in the caption. The most attended words allowed us to interpret whether the model would make relevant changes.

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c}
\hline
\multicolumn{7}{c}{\textbf{COCO (before sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Search} & Image Similarity \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 \\ % - & - & - & - & - & 0.08
\hline
Fully-conn. VAE (L2 cost) & 0.7 & 4.6 & 8.7 & 46.8 & 54 & 0.122 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv. VAE (L2 cost) & 0.7 & 4.4 & 8.5 & 46.6 & 54 & \textbf{0.131} \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
Noalign DRAW & \textbf{1.0} & 6.1 & 11.2 & 52.1 & \textbf{48} & 0.114 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
Skipthought DRAW & \textbf{1.0} & \textbf{6.2} & \textbf{11.5} & \textbf{52.5} & \textbf{48} & 0.118 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
Align DRAW & 0.9 & \textbf{6.2} & 11.2 & \textbf{52.5} & \textbf{48} & 0.115 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\end{table}

{\footnotesize
\bibliography{ram-paper}}
